\input{title.tex}

### 2022-05-01 docs/papers/01_manuscript/04_discussion.tex
fix(fix-bad-unicode-in-bodin2017b-and-compile.): compiling by vscode

% 过去的研究总结出87-WAS收效甚微的几个因素：
Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:{S3-3}).
As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.

>>>>

% 过去的研究总结出87-WAS收效甚微的几个因素：
Although previous studies summarised reasons for the non-ideal effect of 87-WAS, few improvements in the 98-UBR indicate that they underestimated influences from the structural changes (\textit{S3 in Supplementary Material} Figure~\ref{fig:S3-3}).
As we have depicted (Figure~\ref{structure}), the institutional shifts twice framed the structure of SESs in the YRB and led to different building blocks, which were also reported in various types of SESs worldwide.
The empirical studies in many different fields also indicate that the structure before 98-UBR (i.e., fragment ecological units are linked to separate social actors) is likely to be mismatched as isolated stakeholders struggle with holistically maintaining interconnected ecosystems
\cite{sayles2017,sayles2019,cai2016,bergsten2019}.
On the contrary, the YRCC, whose authority matched the YRB in scale after the 98-UBR, led to a well-recognized structure for institutional alignments to social-ecological fit and good outcomes.
The effect of the institutional shifts once again demonstrated that it is not easy to have a win-win situation of environment and interests in complex coupled human-nature systems \cite{hegwood2022} which calls for exceptional understanding and caution to the structure of hampering sustainability \cite{bergsten2019, sayles2019}.
